%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SARATH's TODO
% Add lang/framework info to all major projects
% Add a line describing each major project ?
% Get more power verbs (owned) from CP resume
% Make skills more prominent
% Reorder projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sarath S}{Menon}
{
    \urlstyle{same}
    \href{https://www.linkedin.com/in/sarathsme}{linkedin.com/in/sarathsme} \\
    \href{mailto:sarathmenon1993@gmail.com}{sarathmenon1993@gmail.com} | \href{tel:+919048461414} +91 9048 46 1414
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Calicut}
\descript{B.Tech in Computer Science}
\location{Govt. Engineering College, Thrissur, India | June 2015}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
LinkedIn://  \href{https://www.linkedin.com/in/sarathsme}{\custombold{Sarath S Menon}} \\
Stack Overflow://  \href{https://stackoverflow.com/users/6498687/sarath-s-menon}{\custombold{Sarath S Menon}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical}
\location{Over 2 years:}
C\# \textbullet{} Angular 2+ \textbullet{} JavaScript \textbullet{} .NET \textbullet{} SQLServer \\ 
\location{Over 6 months:}
Java \textbullet{} Android \textbullet{} React Native  \textbullet{} Spring \textbullet{} Groovy \textbullet{} Grails \\
\location{Familiar:}
.NET Core \textbullet{} ReactJs \textbullet{} Shell Script \textbullet{} MySQL \textbullet{} PostgreSQL 
\sectionsep

\subsection{Languages}
English \textbullet{} Hindi \textbullet{} Malayalam
\sectionsep


\section{Interests}
\subsection{Technical}
Machine learning \textbullet{} Data analytics \textbullet{} Analysis of algorithms and optimization \textbullet{} Microservices
\sectionsep Accessibility Evangelist

\subsection{Others}
Politics \textbullet{} Environmentalism \textbullet{} Football (Soccer) \textbullet{} Swimming \textbullet{} Movies 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{RCKR Software Pvt. Ltd.}
\descript{| Software Engineer }
\location{Aug 2015 – Present (4 years 6 months) | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Led the design and development of an e-Book e-commerce web application in Java and angular 2+
    % TODO: Change below line
    \item R&D, prototyping and estimation of prospective products
    \item Full stack web development in a health application using .NET Web API and Angular 2+
    \item Development of a webinar organizer using Grails web framework 
    \item Android app development and optimizations
    
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Major Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Major Projects}

\runsubsection{Instant PHR and CHBase}\\
\descript{Multi-tenant CMS driven health data repository for patient engagement}
\begin{tightemize} 
    \item Designed the architecture for a .NET Web API - Angular 2+ application to replace the legacy .NET Web forms product.
    \item Designed and executed the migration of existing user data from the legacy application to the revamped product.
    \item Designed and developed a SAML 2.0 based Single sign on plugin.
    \item Stabilized and improved the performance of the legacy Instant PHR Android application
\end{tightemize}
\sectionsep

\runsubsection{E-book e-commerce system}
\descript{| Multi tenant CMS driven web application}
\begin{tightemize}
% TODO: Ask Rahul CP
    \item Led a team of 7 in the design and development of the application using microservice architecture.
    \item Designed a CMS driven angular website with ability to add/modify pages from an admin UI. 
    \item Developed a multi-tenant architecture so that multiple clients can work on the same backend and database.
\end{tightemize}
\sectionsep


\runsubsection{Public information system for US Govt. Agency}\\
\descript{Cross platform React Native application}
\begin{tightemize}
    \item Developed a cross platform React native application for public information display
    \item Developed features for complaints, feedback, news bulletins etc.
\end{tightemize}
\sectionsep

\runsubsection{Liveguide}
\descript{| Grails framework based webinar scheduler}
\begin{tightemize}
    \item A webinar scheduler used by marketing teams in academic institutions
    \item Owned and maintained the project for 3 years.
    \item Handled all phases of development(except QA) including solution architecture, development, deployment, server maintenance etc.
\end{tightemize}
\sectionsep

\runsubsection{E-YANTRA 2013}
\descript{| Fertilizer robot | Embedded C}
\begin{tightemize}
    \item Firebird V robot programmed to follow black line grids.
    \item Find shortest path to fertilize plants on the grid, traverses the path and fertilizes each plant.
\end{tightemize}
\sectionsep

% \runsubsection{Video Book Reader}
% \descript{| Android application}
% \begin{tightemize}
%     \item Revamped an existing android Video book reader with modern UI.
%     \item Stabilised and restructured the application.
% \end{tightemize}
% \sectionsep

% \runsubsection{PriFact - School Management System}
% \descript{| .NET Web forms}
% \begin{tightemize}
%     \item Designed the architecture for a Role Permission based access control system
%     \item Developed a tree shaker application to prune unused files in a .NET web forms application.
% \end{tightemize}
% \sectionsep

% \runsubsection{Water treatment monitoring}
% \descript{| Angular 2+ and D3}
% \begin{tightemize}
%     \item Developed feature to display stats (graphs, gauges etc) for various metrics(pressure, temperature) involved in the process using D3.js
%     \item Designed and developed a feature for efficient error handling and logging
% \end{tightemize}
% \sectionsep

% \runsubsection{Forms Builder}
% \descript{| Web library to design complex forms}
% \begin{tightemize}
%     \item Java - Angular 8 NPM library to design and consume complex forms
%     \item Designed and implemented the architecture for the library involving JSON driven form components
% \end{tightemize}
% \sectionsep


\end{minipage}
\end{document}